# pre-class


Make sure you commit this often with meaningful messages. 




### Question 1:

Using a loop, print the integers from 1 to 50. 
```{r}
for (i in 1:50){
  print(i)
}
```

### Question 2:

A.  Using a loop, add all the integers between 0 and 1000.
```{r}
sum_int=0
for (i in 1:1000){
  sum_int=sum_int+i
}
print(sum_int)
```

B. Now, add all the EVEN integers between 0 and 1000 (hint: use seq())
```{r}
sum_int=0
even_int=seq(0,1000,2)
for (i in even_int){
  sum_int=sum_int+i
}
print(sum_int)
```
C. Now, repeat A and B WITHOUT using a loop.
```{r}
vec_int=0:1000
sum_int_all=sum(vec_int)
vec_int_even=seq(0,1000,2)
sum_int_even=sum(vec_int_even)
print(sum_int_all)
print(sum_int_even)
```
### Question 3:

Here is a dataframe of survey data containing 5 questions :

```{r, eval=FALSE}
survey <- data.frame(
                     "participant" = c(1, 2, 3, 4, 5, 6),
                     "q1" = c(5, 3, 2, 7, 11, 0),
                     "q2" = c(4, 2, 2, 5, -10, 99),
                     "q3" = c(-4, -3, 4, 2, 9, 10),
                     "q4" = c(-30, 5, 2, 23, 4, 2),
                     "q5" = c(88, 4, -20, 2, 4, 2)
                     )
```
The response to each question should be an integer between 1 and 5. Obviously, we have some bad values in the dataframe. The goal of this problem is to fix them.

A. Using a loop, create a new dataframe called survey.clean where all the invalid values (those that are not integers between 1 and 5) are set to NA.

B. Now, again using a loop, add a new column to the dataframe called “invalid.answers” that indicates, for each participant, how many bad answers they gave.