# pre-class


Make sure you commit this often with meaningful messages. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```{r}
# The f1 function checks wether the inputted string begins with the inputted prefit. I'm changing the name to prefix_match 
prefix_match <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}

# The f2 function takes a vector as an input, and returns the vector excluding the last element. I'm changing the name to remove_last 
remove_last <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}

# The f3 function replicates y, where the number of replications set by length(x). This can be useful when we want to make y fit the dimensions of x. I'm changing the name to match_length 
match_length <- function(x, y) {
  rep(y, length.out = length(x))
}
```

2. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?
# The difference between rnorm and MASS::mvrnorm() is that the former uses sigma-squared (the sd), while the latter (in the univariate case) uses the sigma (the variance). To make them consistent, first you need to set a seed. Then, we'll define a function which gives equivalent results:
```{r}
random_equiv=function(n,mean,sd,seed=1) {
  x=matrix(0,nrow=n,ncol=2)
  set.seed(seed)
  x[,1]=rnorm(n,mean=mean,sd=sd)
  set.seed(seed)
  x[,2]=MASS::mvrnorm(n,mu=mean,Sigma=sd^2)
  colnames(x)= c("rnorm","mvrnorm")

  return(x)
}
```


3. Use `lapply()` and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset. 
```{r}
lapply(mtcars, function(x)  sd(x)/mean(x))
```

4. Use vapply() to:
    a. Compute the standard deviation of every column in a numeric data frame.
```{r}
# I'm using mtcars as an example of a numeric data frame
numeric_data=mtcars
vapply(numeric_data,function(x)  sd(x),numeric(1))
```
    
    b. Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you’ll need to use vapply() twice.)
```{r}
# I'm creating an example of a mixed data frame, by adding a column of strings to mtcars
library(dplyr)
charac=rep("charac",nrow(mtcars))
mixed=mtcars
mixed$charac=charac
mixed_num=select_if(mixed, is.numeric)
#numeric= unlist(sapply(mixed,is.numeric)
#mixed_num=mixed[,numeric]
vapply(mixed_num,function(x)  sd(x),numeric(1))

```
    
